---
title: "WUP_04"
author: "Put your name here!"
date: "fall 2020"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(knitr)
require(tidyverse)
require(tigerstats)

mydata<-read_csv(file="GSScsv.csv")
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

The data is in the file GSScsv.csv and came from the 2018 General Social Survey.  The question to answer is to resolve this hypothesis.  
$H_0$ There is no difference between the average score on the WORDSUM test and level of schooling DEGREE  
$H_a$ There is a significant difference in average score on the WORDSUM test between at least two levels of DEGREE  

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
basicCN <- ggplot(mydata,aes(x=DEGREE,y=WORDSUM))
```
```{r}
basicCN + geom_boxplot()
```

The GG Boxplot seems to indicate that the graduate level students seemed to perform better on the WORDSUM game, evidenced by the 25th percentile, the 75th percentile, and the median (the latter two are equal).  In some cases, the median for the Graduate level students are as high as the 75th percentiles of the other students.  For the high school/junior high school/LT high school students, the median and 75th pecntiles were lower, indicating those with lesser degrees seemed to do less well on the WORDSUM game.



### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->


```{r}
favstats(WORDSUM~DEGREE,data=mydata)
```
The Graduate students outranked the other classes of students through Q1, median, and mean, suggesting that those with more education tended to do more well on the WORDSUM game.  In contrast, the LT High School and High School students seemed to yield the lowest mins, Q1, medians, Q3, and means, implying that students earlier on in their education might not do as well on the WORDSUM game.


## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
